---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcolorutils

<!-- badges: start -->
<!-- badges: end -->


This package is designed to help you work with R's built-in colors.

## Installation

rcolorutils isn't on CRAN, so you'll need to install it with from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("smach/rcolorutils")
```

## What You Can Do

You can see searchable table with all colors with the `create_color_table()` function. Lone argument is the length of the table page, which defaults to 25.

```{r}
library(rcolorutils)
create_color_table(page_length = 10)

```


rcolorutils also has functions to help you find built-in colors that are similar to one specific color. It's especially useful to answer a question like "what other blues are built in to R"?

The `nearRcolor()` function will return a vector of nearby colors:

```{r }
nearRcolor("skyblue")
```

```{r }
nearRcolor("tomato")
```

If you'd like to _see_ the colors, wrap the results of `nearRcolor()` in the `plotCol()` function:

```{r }
plotCol(nearRcolor("skyblue"), nrow = 2)
```

```{r }
plotCol(nearRcolor("tomato"), nrow = 3)
```

Note that the scales package's `show_col()` function is another way to display the colors:

```{r }
scales::show_col(nearRcolor("green"))
```

If you don't get enough colors, increase the distance.

```{r }
plotCol(nearRcolor("darkgreen"))
```

You may have to fiddle with the distance number to get what you want.

```{r }
plotCol(nearRcolor("darkgreen", "rgb", dist = 80))
```
