---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rcolorutils

<!-- badges: start -->
<!-- badges: end -->


This package is designed to help you find colors that are similar to one specific color. It's especially useful to answer a question like "what other blues are built in to R"?

## Installation

This package is not on CRAN, so you need to install it with from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("smach/rcolorutils")
```
## Examples


The `nearRcolor()` function returns a vector of nearby colors:

```{r }
library(rcolorutils)
nearRcolor("skyblue")
```

```{r }
nearRcolor("tomato")
```

If you'd like to _see_ the colors, wrap the results of `nearRcolor()` in the `plotCol()` function:

```{r }
plotCol(nearRcolor("skyblue"))
```

```{r }
plotCol(nearRcolor("tomato"))
```

Note that the scales package's show_col() function is another way to display the colors:

```{r }
scales::show_col(nearRcolor("green"))
```

If you don't get enough colors, increase the distance.

```{r }
plotCol(nearRcolor("darkgreen"))
```

You may have to fiddle with the distance number to get what you want.

```{r }
plotCol(nearRcolor("darkgreen", "rgb", dist = 80))
```
