---
title: "Using this package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using this package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rcolorutils)
```

This package is designed to help you work with R's built-in colors.

You can enerate a searchable table with all colors with the `create_color_table()` function. The function's only argument is the length of the table page, which defaults to 25. 

With columns for red, green, and blue, you can sort and filter the table by rgb color attributes as well as color name or hex code. 

```{r}
create_color_table(page_length = 10)
```


rcolorutils also has functions to help you find built-in colors that are similar to one specific color. It's especially useful to answer a question like "what other blues are built in to R"?

The `nearRcolor()` function will return a vector of nearby colors:

```{r }
nearRcolor("skyblue")
```

```{r }
nearRcolor("tomato")
```

If you'd like to _see_ the colors, wrap the results of `nearRcolor()` in the `plotCol()` function:

```{r fig.width=8}
plotCol(nearRcolor("skyblue"), nrow = 2)
```

```{r }
plotCol(nearRcolor("tomato"), nrow = 3)
```

Note that the scales package's `show_col()` function is another way to display the colors:

```{r }
scales::show_col(nearRcolor("green"))
```

If you don't get enough colors, increase the distance.

```{r }
plotCol(nearRcolor("darkgreen"))
```

You may have to fiddle with the distance number to get what you want.

```{r }
plotCol(nearRcolor("darkgreen", "rgb", dist = 80))
```
