---
title: "Using this package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using this package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rcolorutils)
```

This package is designed to help you work with R's built-in colors.

You can see a searchable table with all colors by running the `create_color_table()` function.

```{r}
create_color_table()
```


rcolorutils also has functions to help you find built-in colors that are similar to one specific color. It's especially useful to answer a question like "what other blues are built in to R"?

The `nearRcolor()` function will return a vector of nearby colors:

```{r }
nearRcolor("skyblue")
```

```{r }
nearRcolor("tomato")
```

If you'd like to _see_ the colors, wrap the results of `nearRcolor()` in the `plotCol()` function:

```{r fig.width=8}
plotCol(nearRcolor("skyblue"), nrow = 2)
```

```{r }
plotCol(nearRcolor("tomato"), nrow = 3)
```

Note that the scales package's `show_col()` function is another way to display the colors:

```{r }
scales::show_col(nearRcolor("green"))
```

If you don't get enough colors, increase the distance.

```{r }
plotCol(nearRcolor("darkgreen"))
```

You may have to fiddle with the distance number to get what you want.

```{r }
plotCol(nearRcolor("darkgreen", "rgb", dist = 80))
```
